---
title: "Output 1"
author: "MLG"
format: html
editor: visual
---


## Setting up the libraries

```{r}
library(tidyverse)
library(here)
library(tsibble)
library(feasts)
library(fable)
```

## Loading the utility consumption dataset

```{r}
utility_consum_df <- read_csv(here('data/output 1/elec_by_utility_ca.csv')) %>% 
  janitor::clean_names()

## To see the total consumption per year residential sector
aggregated_utility_consum <- utility_consum_df %>%
  filter(utility_type == 'Investor owned utility') %>% 
  group_by(year) %>%
  summarize(total_residential = sum(residential))

```

## Loading the nem capacity dataset

```{r}

nem_capacity_df <- read_csv(here('data/output 1/nem-capacity-chart.csv')) %>% 
  janitor::clean_names() %>% 
  rename(year = category) %>% 
  mutate(year = as.integer(year))

all_years <- data.frame(year = c(1990:2023))


# Merge datasets
utility_nem_df <- merge(all_years, aggregated_utility_consum,
                        by = "year", all.x = TRUE) %>%
                  left_join(nem_capacity_df, by = "year") 

utility_nem_df$total_usage_mw <- utility_nem_df$total_residential * 1000

# Plotting the time series with secondary axis
plot_residential <- ggplot(utility_nem_df, aes(x = year, y = total_usage_mw)) +
  geom_line(color = "blue", size = 1) +
  labs(x = "Year", y = "Residential Consumption (MW)") +
  theme_minimal()

# Plotting NEM capacity
plot_nem <- ggplot(utility_nem_df, aes(x = year, y = prior_years_capacity)) +
  geom_line(color = "red", size = 1) +
  labs(x = "Year", y = "NEM Capacity (MW)") +
  theme_minimal()


# Combine plots into a grid
library(cowplot)
combined_plot <- plot_grid(plot_residential, plot_nem, nrow = 1)
print(combined_plot)

```
##

```{r}
ts_data <- ts(utility_nem_df$total_residential, start = c(1990), frequency = 1)

plot_trends <- ggplot(data = data.frame(year = time(ts_data), total_residential = ts_data), aes(x = year, y = total_residential)) +
  geom_line() +
  labs(title = "Residential Energy Consumption Trends in California") +
  theme_minimal()

plot_trends

```


## Group 1: 3 utilities and Group 2: Other IOUs, look at slope of linear regression across both the groups, compare the slopes to see the statistical different. Is there difference ? Is there simple linear regression


- Set of A utilities , in Linear Regression take a interaction terms between utility group A or B  ~ year |f1 <-  energy consum ~ year + group
f2<- energy consum ~ year * group 

- Give a mechanistic reason for why 
